---
title: "Business Intelligence Project"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |                             |
|--------------------------------------------|----------------------------|
| **Student ID Number**                        | 119630,135844,131038,104135 |
| **Student Name**                             | beasts                      |
| **BBIT 4.2 Group**                           | A&B&C                       |
| **BI Project Group Name/ID (if applicable)** | beasts                      |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

## Load dataset

```{r}
insurance <- read.csv("data/insurance_info.csv")

```

# Handle missing values ----

### Are there missing values in the dataset?

```{r}
library(tidyverse)

anyNA(insurance)
```

### How many?

```{r}
library(naniar)

n_miss(insurance)
```

### What is the proportion of missing data in the entire dataset?

```{r}
prop_miss(insurance)
```

### What is the number and percentage of missing values grouped by each variable?

```{r}
miss_var_summary(insurance)
```

### Which variables contain the most missing values?

```{r}
gg_miss_var(insurance)
```

## Remove the observations with missing values ----

```{r}
insurance_obs <- insurance %>% filter(complete.cases(.))
dim(insurance_obs)
```

#### Are there missing values in the dataset?

```{r}
any_na(insurance_obs)
```

# Exploratory Data Analysis

### Dimensions

```{r}
# display the dimensions of your datasets
dim(insurance_obs)
#Identify the Data Types
sapply(insurance_obs, class)
```

## Descriptive Statistics

### Measures of frequency

```{r}
insurance_obs_freq <- insurance_obs$age
cbind(frequency = table(insurance_obs_freq),
      percentage = prop.table(table(insurance_obs_freq)) * 100)
```

### Measures of central tendency

```{r}
insurance_obs_mode <- names(table(insurance_obs$age))[
  which(table(insurance_obs$age) == max(table(insurance_obs$age)))
]
print(insurance_obs_mode)
```

### Measures of distribution

#### Measure the variance of the age variable

```{r}
var(insurance_obs[, 6])

```

#### Measure the standard deviation of age variable

```{r}
sd(insurance_obs[, 6] )
```

#### Measure the kurtosis of each age variable

```{r}
library(moments)

kurtosis(insurance_obs[, 6], na.rm = TRUE)
```

#### Measure the skewness of each variable

```{r}
skewness(insurance_obs[, 6])
```

### Measures of relationship

#### Measure the covariance between variables

```{r}
insurance_obs_cov <- cov(insurance_obs[,c(2, 6)])
View(insurance_obs_cov)
```

#### Measure the correlation between variables

```{r}
insurance_obs_cor <- cor(insurance_obs[, c(2, 6)])
View(insurance_obs_cor)
```

## Inferential statistics

### Perform ANOVA

#### One-Way ANOVA

```{r}
insurance_obs_one_way_anova <- aov(age ~ rating, data = insurance_obs)
summary(insurance_obs_one_way_anova)
```

#### Two-Way ANOVA

```{r}
insurance_obs_additive_two_way_anova <- aov(age ~ rating + packagePrice, # nolint
                                           data = insurance_obs)
summary(insurance_obs_additive_two_way_anova)
```

## Basic Visualization

### Univariate plots

#### create histograms

```{r}
par(mar = c(4, 4, 2, 2)) 

insurance_obs_yield <- as.numeric(unlist(insurance_obs[, 6]))
hist(insurance_obs_yield, main = names(insurance_obs)[6])

```

#### Create Box and Whisker Plots for Each Numeric Attribute

```{r}
boxplot(insurance_obs[, 6], main = names(insurance_obs)[6])
boxplot(insurance_obs[, 2], main = names(insurance_obs)[2])
boxplot(insurance_obs[, 8], main = names(insurance_obs)[8])
```

#### Create Bar Plots for Each Categorical Attribute

```{r}
barplot(table(insurance_obs[, 3]), main = names(insurance_obs)[3])
```

### Multivariate Plots

#### Create a Correlation Plot

```{r}
library(corrplot)

corrplot(cor(insurance_obs[, c(2, 6)]), method = "circle")
```

## Qualitative Data Analysis

### Customize the Visualizations, Tables, and Colour Scheme

#### blue-grey colour scheme for the visualizations

```{r}
blue_grey_colours_11 <- c("#27408E", "#304FAF", "#536CB5", "#6981c7", "#8da0db", "#dde5ec", "#c8c9ca", "#B9BCC2", "#A7AAAF", "#888A8E", "#636569")

blue_grey_colours_6 <- c("#27408E", "#304FAF", "#536CB5", "#B9BCC2", "#A7AAAF", "#888A8E")

blue_grey_colours_4 <- c("#27408E", "#536CB5", "#B9BCC2", "#888A8E")

blue_grey_colours_2 <- c("#27408E", "#888A8E")

blue_grey_colours_1 <- c("#6981c7")
```

#### Custom theme for visualizations

```{r}
blue_grey_theme <- function() {
  theme(
    axis.ticks = element_line(
                              linewidth = 1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    axis.text = element_text(
                             face = "bold", color = "#3f3f41",
                             size = 12, hjust = 0.5),
    axis.title = element_text(face = "bold", color = "#3f3f41",
                              size = 14, hjust = 0.5),
    plot.title = element_text(face = "bold", color = "#3f3f41",
                              size = 16, hjust = 0.5),
    panel.grid = element_line(
                              linewidth = 0.1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    panel.background = element_rect(fill = "#f3eeee"),
    legend.title = element_text(face = "plain", color = "#3f3f41",
                                size = 12, hjust = 0),
    legend.position = "right"
  )
}
```

#### Customize the text tables for consistency using HTML formatting

```{r}
kable_theme <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  full_width = FALSE)
}
```

### Contractions

#### removal of special characters and conversion of lowercase

```{r}
remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z0-9 ]", "", doc, ignore.case = TRUE)
}


insurance_obs$preIllness <- sapply(insurance_obs$preIllness, tolower) # nolint
insurance_obs$services <- sapply(insurance_obs$services, tolower) # nolint
insurance_obs$packageType <- sapply(insurance_obs$packageType, tolower) # nolint
insurance_obs$priceRage <- sapply(insurance_obs$priceRage, tolower) # nolint
View(insurance_obs)
```

# Pre-prosessing and Data Transformation

# Training the Model

# Hyper-parameter Tuning and Ensembles

# Consolidation
